\PaperTitle

### 2024-05-04 Final_Report/paper.tex

\subsection{Employed models}
For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet. We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network. The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution. 
These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet. We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
\subsubsection{Logistic Regression (Baseline)}

>>>>

\subsection{Employed models}
For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet. We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network. The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution. 
These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet. We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
\subsubsection{Logistic Regression (Baseline)}
As a starting point, we employed the Logistic Regression model as a baseline for our data analysis. Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
It was understoof initiallly that this model may not be an ideal fit for our data, due to the regressions binary nature having more than two classifications is not ideal.
However, for our purposes this was an excellent baseline. It was important for us to first visualize what features define network traffic so that we could further model around them, and the logistic regression was the most efficient choice for that.
Our model returned us an accuracy score of .56, or 56\%, which is less than ideal but not entirely unexpected.
To analyze the data further, we put the results from our model into a confusion matrix. With this we were able to see that the model predicted Blackboard quite well, atleast in comparison to ChatGPT and Linkedin which were far poorer.
